\ttitle

### 2013-01-30 Chapters/Chapter2.tex
Added text on clustering

Data clustering can be used with two different applications, exploratory or 
confirmatory \cite{jain1999data}. In the former, the purpose is to discover 
clusters in a point cloud of data points. Here the cluster is defined as a 
group of homogeneous data points measured by some coherence measure, often a 
distance function with the data points being defined as vectors. The produced 
clusters, which are a representation of the data examined, can be used in the 
latter application to assign new provided data points to a cluster and thereby 
classify them.

Depended on the precise setup, clustering can be used as a successive step 
after or an implementation of temporal segmentation. When temporal 
segmentation is used to create successive coherent data points, clustering can 
be used to recognize the same activities in different points of time. The data 
points provided to the clustering will be some representation of each segment 
and each segment will be labeled with a activity. An other mechanism could be 
to extract features from the raw data points and use these to create clusters 
directly *** [temporal modifications]. Both mechanisms requires the 
exploratory and confirmatory phases.

@@

The most critical step, the \emph{grouping},

>>>>

Data clustering can be used with two different applications, exploratory or 
confirmatory \cite{jain1999data}. In the former, the purpose is to discover 
clusters in a point cloud of data points. Here the cluster is defined as a 
group of homogeneous data points measured by some coherence measure, often a 
distance function with the data points being defined as vectors. The produced 
clusters, which together form a representation of the data examined, can be 
used in the 
latter application to assign new provided data points to a cluster and thereby 
classify them.

Depended on the precise setup, clustering can be used as a successive step 
after or an implementation of temporal segmentation. When temporal 
segmentation is used to create successive coherent data points, clustering can 
be used to recognize the same activities in different points of time. The data 
points provided to the clustering will be some representation of each segment 
and each segment will be labeled with a activity. Another mechanism could be 
to extract features from the raw data points and use these to create clusters 
directly *** [temporal modifications]. Both mechanisms requires the 
exploratory and confirmatory phases.

@@

In the most critical step, the \emph{grouping}, the data points with the 
highest coherence are linked together to form a cluster. The result can be a 
hard partition over the data or a fuzzy membership degree to each cluster for 
each data point. When applying rules for merging and splitting cluster, a 
hierarchical partition is constructed. Partitional clustering algorithms 
assign data points to clusters by optimizing some criterion, e.g. the mean 
squared distance from each data point to the clusters' centroid.

Especially in case of large data sets, the resulting clusters will be defined 
by many data points. To form a compacter and simpler representation, 
\emph{abstraction} can be used. This will simply analysis by humans or 
automated systems. A common abstraction is to use the clusters' centroid 
\cite{diday1976clustering} or parameters of Gaussian patterns.

The final step which can be applied to the resulting partition is some 
\emph{qualification}. The quality of multiple partitions can be compared and 
the validity of the partition can be determined. A partition is valid if 
reasonably it could not been constructed by change or as some random process. 
External references of models can be used to compare, or the internal data 
points can be examined. *** [better wordings]
